Local connections

### 2023-04-07 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd
Plot discrete and continuous predictions across groups

Updated 12/15/2022

@@

```{r}
model_control <- lm(geo_scope_num ~ work_field_code1 + local_connect + psu_level + province_code, data = ongo)
summary(model_control)
```

>>>>

Updated 03/24/2023

@@

```{r}
model_control <- lm(geo_scope_num ~ work_field_code1 + local_connect + local_aim + psu_level + province_code, data = ongo)
summary(model_control)
```

### 2023-04-07 notebook/analysis-local.qmd
Plot discrete and continuous predictions across groups

TODO: Prop of 1s, 32s, and in-betweens

>>>>

```{r plot-pred-discrete-continuous-local, message=FALSE}
preds_local_plot <- preds %>% 
  ungroup() %>% 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, local_connect) %>% 
  summarize(count = n()) |> 
  group_by(local_connect) |> 
  mutate(prop = count / sum(count))

ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
  geom_segment(aes(xend = local_connect, yend = 0), color = "grey50") +
  geom_point(color = clrs[2], size = 2) +
  expand_limits(y = 0) +
  facet_wrap(vars(outcome)) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions") +
  theme_ongo()
```
